---
title: "WineQuality"
output: html_document
---

Setting the Packages
----------------------
```{r}
#library('RSNNS')
library('neuralnet')
library('ggplot2')
```

Reading in the Data
------------------------
```{r}
data = read.csv('winequality-white.csv')

#View the structure of the dataframe
str(data)
summary(data)

#Scatter plot of the Quality variable
plot(data$quality)
```
From the scatter plot we see that Data Quality, which we are wanting to predict, is quite thin at the ends.
We are then wanting to bin Quality into 3 bins, 1, 2, 3

Binning Quality
-----------------------
```{r}
attach(data)
data$quality_bin[quality < 5] <- 1
data$quality_bin[quality > 4 & quality < 7] <- 2
data$quality_bin[quality > 6] <- 3
View(data)
plot(data$quality_bin)
```

For Plot's sake
-----------------------
To read up on the full documentation on ggplot2 - http://docs.ggplot2.org/current/
```{r}
#factor the quality_bin. This factor is useful for later modeling and also plotting with qplot
data$quality_bin <- factor(x = data$quality_bin, labels=c("1","2","3"))

qplot(data$quality_bin, data$fixed.acidity, data=data, geom = c("boxplot", "jitter"), 
      fill=data$quality_bin, main="Quality by Fixed Acidity", xlab="Quality", ylab="Fixed Acidity")

qplot(data$quality_bin, data$volatile.acidity, data=data, geom = c("boxplot", "jitter"), 
      fill=data$quality_bin, main="Quality by Volatile Acidity", xlab="Quality", ylab="Fixed Acidity")

qplot(data$quality_bin, data$citric.acid, data=data, geom = c("boxplot", "jitter"), 
      fill=data$quality_bin, main="Quality by Citric Acidity", xlab="Quality", ylab="Fixed Acidity")
```

Building the model
---------------------------
Finally we get to build the model! 
Our model is used to solve a Classification problem. We are going to use a NN first.
1) We will use a 80/20 Train/Test to build and test the model
2) Analyzing the result using crosstab
3) We'll be using the RSNNS package to build the model
```{r}
attach(data)
Var = c("fixed.acidity", "volatile.acidity","citric.acid","residual.sugar","chlorides","free.sulfur.dioxide","total.sulfur.dioxide","density", "pH", "sulphates","alcohol")

# Scale the data
data_scaled <- cbind(scale(data[Var]),data["quality_bin"])
View(data_scaled)

#Split train and test
library(caret)
set.seed(3456)
trainIndex <- createDataPartition(data$quality_bin, p = .8,
                                  list = FALSE,
                                  times = 1)
head(trainIndex)
tail(trainIndex)

train <- data_scaled[trainIndex, ]
test <- data_scaled[-trainIndex, ]
m <- model.matrix(~Var, data = data_scaled)
head(m)
#fit <- neuralnet(quality_bin ~ fixed.acidity+volatile.acidity+citric.acid+residual.sugar+chlorides+free.sulfur.dioxide+total.sulfur.dioxide+density+pH+sulphates+alcohol, train, hidden = 10, threshold = 0.01, lifesign = 'full')


```